---
title: "hw4"
author: "Tanupat Boonchalermvichien"
date: "February 6, 2020"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## load packages and data

```{r}
library(igraph)
library(igraphdata)
library(CINNA)
library(car)
data("yeast")
tab <- degree(yeast) %>% table()
plot(tab)
```

## find centralities including barycenter, closeness, betweeness, average distance, information, eigenvector, leverage, markov, harmonic, degree 

```{r}
yeast_sub <- induced_subgraph(yeast, V(yeast)[components(yeast)$membership ==1])
pr_cen <- proper_centralities(yeast_sub)
pr_cen
bary_cen <- calculate_centralities(yeast_sub, include = pr_cen[4])
avg_dist <- calculate_centralities(yeast_sub, include = pr_cen[3])
info_cen <- calculate_centralities(yeast_sub, include = pr_cen[44])
names(info_cen[[1]]) <- names(bary_cen[[1]]) 
lever_cen <- calculate_centralities(yeast_sub, include = pr_cen[35])
harmonic_cen <- calculate_centralities(yeast_sub, include = pr_cen[47])
markov_cen <- calculate_centralities(yeast_sub, include = pr_cen[24])
eigen_cen <- calculate_centralities(yeast_sub, include = pr_cen[15])
close_cen <- calculate_centralities(yeast_sub, include = pr_cen[7])
degree_cen <- calculate_centralities(yeast_sub, include = pr_cen[10])
between <- betweenness(yeast_sub)
between_cen <- c()
between_cen$'Betweeness centrality' <- between
#pca <- pca_centralities(calc_cen, scale.unit = TRUE)
#tsne <- tsne_centralities(calc_cen, dims = 2, perplexity = 1, scale= TRUE
```

## plot graph of each type of centrality labeled in red 
```{r}

plotgraph <- function(graph, centrality, num, normalize =TRUE){
  size <- centrality[[1]]
  if (normalize == TRUE){
    size <- (size-min(size))*5/(max(size)-min(size))
  }
  vertex <- sort(size, decreasing = TRUE, index.return = TRUE)$ix[1:num]
  V(graph)[vertex]$color <- 'red'
  V(graph)[-vertex]$color <- 'white'
  plot(graph, 
       vertex.label = NA,
       vertex.size = size,
       #layout = layout.davidson.harel(graph),
       layout = layout.reingold.tilford(graph,params=list(root=2)),
       main = names(centrality))
}


plotmultiple <- function(graph,list,column, num, multiple=TRUE){
  if (multiple==TRUE){
      par(mfrow=c(length(list)%/%column+1, column))
  }
  for(a in list){
    plotgraph(graph, a, num)
  }
}

ourlist = list(close_cen,degree_cen,eigen_cen, between_cen, bary_cen, avg_dist, info_cen,lever_cen,harmonic_cen,markov_cen)
#ourlist = list(close_cen,eigen_cen, between_cen)
plotmultiple(yeast_sub, ourlist,4, 50, multiple= FALSE)

```

## try compare intersect of most important centrality vertices from each type of centrality 

```{r}
center <- as.data.frame(matrix(c(NA)*100, nrow = 10, ncol=10))
for (i in 1:length(ourlist)){
  b<- sort(ourlist[[i]][[1]], decreasing= TRUE, index.return = TRUE )[[2]][1:10]
  center[[i]] <- b
}
name <- unlist(lapply(ourlist, names))
names(center) <- name

e <- matrix(c(NA)*100, nrow=10,ncol=10)
for (i in 1:length(center)){
  for (j in 1:length(center)){
    e[j,i]<-length(intersect(center[[i]],center[[j]]))
  }
}
rownames(e) <- name
colnames(e) <- name
heatmap(e)
```

## find degree and average distance of each vertices 

```{r}
# average degree
deg <- apply(center,2, function(x) mean(degree(yeast_sub)[x]))%>%
  sort(decreasing = TRUE)
deg
# closeness
close <- apply(center,2, function(x) mean(closeness(yeast_sub)[x])) %>%
  sort(decreasing =TRUE)
close
```




## find correlation between each type of centrality 
```{r}
visualize_correlations(ourlist, 'pearson')
df <- as.data.frame(ourlist)
col_name <- colnames(df)
cor_mat <- cor(df)
corrplot::corrplot(cor_mat)
scatterplotMatrix(cor_mat)

```


