---
title: "hw5"
author: "Tanupat Boonchalermvichien"
date: "February 19, 2020"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### According to the exercise “Network Structure and Similarity (NetStru_Rlab)”, answer the following questions which are the same as written in the exercise.

## According to the given network, what is the maximal subgraph in which every vertex has at least degree 1, 2, 3, 4, or 5?
```{r}
library(igraph)

adj <- matrix(
  c(0,1,0,1,1,1,0,
    1,0,0,1,0,1,1,
    0,0,0,1,0,0,0,
    1,1,1,0,0,1,1,
    1,0,0,0,0,1,0,
    1,1,0,1,1,0,1,
    0,1,0,1,0,1,0), 
  nrow=7, ncol=7,
  byrow=TRUE,
  dimnames = list(c('A','B','C','D','E','F','G'),
                  c('A','B','C','D','E','F','G'))
)

g <- graph.adjacency(t(adj), mode='undirected')
plot(g, layout = layout_nicely)
```

```{r}
c = coreness(g)
for (i in 1:max(c)){
  cat('maximum subgraph with',i,'degrees has', sum(c>=i), 'vertices\n')
}
```

## Fix the function ‘getMotifs’ to get the correct number of motifs.

```{r}
motifs(g, 3)
# [1] NA NA 12  8
motifs(g, 4)
# [1] NA NA NA NA  1 NA  4 10  0  5  2

getMotifs <- function(mygraph, size=3){
  pattern <- graph.full(size)
  iso <- subgraph_isomorphisms(pattern, mygraph)
  motifs <- lapply(iso, function(x){induced_subgraph(mygraph, x)})
  return(motifs)
}
allmotifs <- getMotifs(g,3)
plot(graph_from_isomorphism_class(3,3,directed=FALSE)) # should have 8 motifs
length(allmotifs)
```

```{r}
getMotifs_fixed <- function(mygraph, size=3){
  pattern <- graph.full(size)
  iso <- subgraph_isomorphisms(pattern, mygraph)
  
  motifs <- lapply(iso, function(x){induced_subgraph(mygraph, x)})
  motifs <- lapply(motifs, function(x){as_ids(E(x))})
  return(unique(motifs))
}
allmotifs_fixed <- getMotifs_fixed(g, 3)

length(allmotifs_fixed) # 8 motifs as same as expected!

```
try generalize function to get all isomorphism class number in our graph with motif size 3 and 4
```{r}
getNumAllMotifs <- function(mygraph, size=3){
  a <- c()
  n <- ifelse(size==3, 3, 10)
  for (i in 0:n){
    pattern <- graph_from_isomorphism_class(size,i,directed = FALSE)
    if (is_connected(pattern)){
    #plot(pattern)
    iso <- subgraph_isomorphisms(pattern, mygraph, method = 'vf2')
    motifs <- lapply(iso,function(x){as_ids(E(induced_subgraph(mygraph, x)))})
    motifs <- unique(motifs)
    b <- sum(unlist(lapply(motifs, function(x){length(x) == gsize(pattern)})))
    } else{
      b <- NA
    }
    a <- append(a, b )
    }
  return(a)
}
cat('This is our result for motif size 3 \n', getNumAllMotifs(g, size=3), '\n')
cat('This is expected for motif size 3: \n',motifs(g, size=3),'\n')
cat('This is our result for motif size 4 \n', getNumAllMotifs(g, size=4), '\n')
cat('This is expected for motif size 4: \n',motifs(g, size=4))
```



## What are the differences among Jaccard, Dice and inverse log-weighted similarities?

jaccard similarity is intersect(A,B)/union(A,B)
Dice similarity is 2v/(ki+kj) if v is number of similar vertices
inverse log-weighted is sum of all vertices (v)  sumv((1/log(kv))*cicj) if ci=1 iff that vertex is a neighbor of vertex i; ci=0 vice versa, kv is degree of vertex v

## How can we calculate node similarity like cosine similarity and correlation in R?

```{r}
library(lsa)
adj_mat <- as.matrix(as_adjacency_matrix(g))
cos <- cosine(adj_mat)
corrplot::corrplot(cos)
heatmap(cos)
```
```{r}
co <- cor(adj_mat)
corrplot::corrplot(co)
heatmap(co)
```
## Interpret the assortativity results and compare them with the random network and the BA network.

```{r}
k = gorder(g)
assortativity_degree(g)
#assortativity_degree(sample_pa(n = k, directed = FALSE))
#assortativity_degree(sample_gnp(n = k, p = gsize(g)/(k*(k-1)/2)))

sim <- function(time= 100, graph_statement){
  a = 0
  for (i in 1:time){
    a = a+ graph_statement
  }
  return(a/time)
}

cat('preferential attachment',sim(100, assortativity_degree(sample_pa(n = k, directed = FALSE))),'\n')
cat('random graph',sim(100, assortativity_degree(sample_gnp(n = k, p = gsize(g)/(k*(k-1)/2)))))
```
preferential attachment has lowest assortativity coefficient
followed by random graph
and our graph g has highest assortativity coefficient
the higher assortativity coefficient means the more high-degree nodes stay together. 